---
title: "Jackdaw Associations"
output: html_document
---

# Introduction

The temporal data comes from Passive Integrated Transponder (PIT)-tagged jackdaws.
The dataset is a series of timestamps (about a 4 week period, from 19th July - 16th August 2015), with corresponding birdID at 
a feeder located in Pencoose farm, Stithians, Cornwall, UK.

| timestamp |  birdID |
|:-----------|:----------|
| 719145756 |  01010C10D357 |
| 719174140 |  02010C11169D | 

The format of the timestamp is month/day/hour/minute/second, so 719145756 is 14:57:56
on 19th July.

**Objective**: *"To identify the underlying social network structure"*

# Read and preprocess data

We start by reading and preprocess the data. Specifically do the following:

1. Convert `birdID` to a unique integer
2. Convert `timestamp` (e.g 719145756) to a `timeObject` (e.g 2015-07-19 14:57:56 GMT)
3. Convert `timeObject` (e.g 2015-07-19 14:57:56 GMT) to a `relativeTime` (e.g 53876) secs since 
the *start* of the first recorded day (e.g 2015-07-19 00:00:00 GMT)

```{r, warning=FALSE, message=FALSE}
# Clear workspace
rm(list = setdiff(ls(), lsf.str())) 

# Load all libraries to be used in subsequent analyses
library(mclust) # Gaussian Mixture Model
library(network) # to draw network
library(RColorBrewer) # color brewer colours

# Read data
data <- read.table(file="data.csv", header=T, sep=",", skip=0)

# Remove prefix 01 or 02 as this only corresponds to one of the two antennas and not a
# different bird, that is, 01010C10D357 and 02010C10D357 are the same bird 010C10D357 
data$fullBirdID <- data$birdID
data$birdID <- as.factor(substring(data$birdID, 3)) # 141 unique birds
# BirdIDs are long e.g 010C10D357, let us shorten them to an integer
uniqueBirdID <- levels(data$birdID) 
iCnt <- 1 # counter for unique birdIDs
for (birdID in uniqueBirdID)
{
    levels(data$birdID)[uniqueBirdID==birdID] = iCnt # new birdID = 1, 2, ..., 155
    iCnt <- iCnt + 1
}

# Convert timestamp to a timeObject
data$timeObject <- paste("0", data$timestamp, sep="") # append a "0" to start of timestamp
data$timeObject <- strptime(data$timeObject, "%m%d%H%M%S", tz="GMT")

# Convert to relative time in secs
timeDatum <- paste("0", data$timestamp[1], sep="") # timestamp[1] = 8/5 05:30:33
substr(timeDatum, start=5, stop=10) <- "000000" # timeDatum = 8/5 00:00:00
timeDatum <- strptime(timeDatum, "%m%d%H%M%S", tz="GMT")
data$relativeTime <- as.numeric(difftime(data$timeObject, timeDatum, units="secs"))
```

# Inter-visitation times

To elucidate on the data's structure let's plot a histogram (on log scale) of the 
inter-visitation times, that is, the time difference between successive bird observations 
(given that they are different birds). We compute these differences separately on 
two weeks chunks of data.

```{r, warning=FALSE, message=FALSE, cache=TRUE, fig.width=7, fig.height=7, fig.align='center'}
N2Weeks <- ceiling(max(data$relativeTime)/60/60/24/7/2) # no. of 2 weeks
N2Weeks <- N2Weeks - 1 # Wk1-2, Wk3-4, but for Wk5 there's only "a bit" of data
legStr <- c() # store legend strings
colours <- brewer.pal(n=N2Weeks, 'Set1')
#pdf("Histogram.pdf")
for (iWeek in seq(N2Weeks))
{
    # Select week data
    startSec <- (iWeek-1)*2*7*24*60*60 # 2wks*7days*24hrs*60mins*60secs 
    stopSec <- (iWeek)*2*7*24*60*60
    thisData <- data[data$relativeTime >= startSec & data$relativeTime < stopSec, ]
    delta <- c() # variable to store inter-visitation times
    for (i in seq(from=2, to=dim(thisData)[1]))
    {
        if (data$birdID[i-1] != data$birdID[i]) # only compute if it's a different bird
        {
            thisDelta <- data$relativeTime[i] - data$relativeTime[i-1]
            if (thisDelta < 12*60*60) # 12hrs*60mins*60s
            {
                delta <- c(delta, thisDelta) # it's a valid delta
            }
        }
    }
    thisHist <- hist(delta, plot=FALSE, breaks=1000)
    if (iWeek==1)
    {
        plot(thisHist$density ~ thisHist$mids, log="xy", col=colours[iWeek], pch=16, 
              xlab="log10(Inter-visitation time) (secs)", ylab="log10(Frequency)", xaxt="n", 
             xlim=c(10, 100000), cex.lab=1.3, cex.axis=1.3, cex.main=1.3, cex.sub=1.3) # plot log scale
    }
    else 
    {
        points(thisHist$density~thisHist$mids, col=colours[iWeek], pch=16)
    }
    legStr <- c(legStr, paste("week", (iWeek*2)-1, '-', (iWeek*2), sep=""))
}
axis(side = 1, at = c(10, 100, 1000, 10000, 100000), cex.axis=1.3)
legend("topright", legStr, bty="n", col=colours, pch=16, cex=1.5)
#dev.off()
```

The histogram suggests that the distribution of inter-visitation times is stable over
different weeks of data. The data is dominated by short inter-visitation periods, corresponding
to feeding events, and then large inactivity periods. Let us visualise these feeding/gathering
events by plotting the first week's observations, split by day.


```{r, warning=FALSE, message=FALSE, cache=TRUE, fig.width=8, fig.height=20, fig.align='center'}
NDays <- 7
par(mfrow=c(NDays, 1))
for (iDay in seq(NDays))
{
    startSec <- (iDay-1)*24*60*60 
    stopSec <- (iDay)*24*60*60
    thisData <- data[data$relativeTime >= startSec & data$relativeTime < stopSec, ]
    plot(thisData$timeObject, rep(1, dim(thisData)[1]), type="h", 
         main=paste("Day", iDay), xlab="Time of day", ylab="Observation", ylim=c(0, 1.05))
}
```

# Social network identification

To infer the underlying social network structure we follow the work of Psorakis et al.
*J. R. Soc. Interface (2012)* The first day of data is used to illustrate the workflow.

## 1) Cluster `relativeTime` and generate the responsibility matrix

As we have seen previously, the data consists of several distinct feeding events. The first 
step is to cluster timestamps into these separate gathering events, such that, temporally
close observations are grouped together. Let $K$ be the total number of clusters, 
we model each timestamp $t$ as a Gaussian Mixture Model (GMM):

$$
p(t) = \sum_{i=1}^K \pi_i \mathcal{N}(t|\mu_i, \sigma^2_i)\ \mathrm{and}\ \sum_{i=1}^K \pi_i = 1
$$

For example if we had 3 feeding events then we fit 3 Gaussian distributions with
different mean and variance. Let us simulate this scenario to illustrate GMM fitting:

$$
p(t) = \pi_1 \mathcal{N}(t|\mu_1, \sigma^2_1) + \pi_2 \mathcal{N}(t|\mu_2, \sigma^2_2) + \pi_3 \mathcal{N}(t|\mu_3, \sigma^2_3)
$$


```{r, warning=FALSE, message=FALSE, cache=TRUE, fig.width=6, fig.height=14, fig.align='center'}
par(mfrow=c(2, 1))
# Simulate data
N <- 100 # 50 observations per gathering event
k <- 3 # no. of simulated events
set.seed(101) # to reproduce results
event1 <- rnorm(n=N, mean=1000, sd=100) # cluster 1
event2 <- rnorm(n=N, mean=1300, sd=50) # cluster 2
event3 <- rnorm(n=N, mean=1800, sd=200) # cluster 3
xTrain <- c(event1, event2, event3) # concatenate data
plot(xTrain, rep(1, N*k), type="h", ylim=c(0, 1.05), xlab="relativeTime (secs)", ylab="Observation", 
     main="Simulated gathering events")    

# Fit Gaussian Mixture Model
fit <- Mclust(data=xTrain, G=k, modelNames="V")

# Evaluate GMM and plot
#pdf("GMM.pdf")
xMin <- min(xTrain)
xMax <- max(xTrain)
xTest <- seq(xMin - 0.1*xMin, xMax + 0.1*xMax, length=(xMax - xMin)*2) # test data to evaluate GMM fit on
pdfX <- matrix(data=NA, nrow=length(xTest), ncol=k) # prob distn function
hist(xTrain, breaks=100, freq=F, col="grey", border="white", xlab="Relative time (secs)", 
     ylab="Probability density", main="", cex.lab=1.3, cex.axis=1.3, cex.main=1.3, cex.sub=1.3)
for (i in seq(k)) {
    p <- fit$parameters$pro[i]
    mu <- fit$parameters$mean[i]
    sigma <- sqrt(fit$parameters$variance$sigmasq[i])
    pdfX[, i] <- p*dnorm(x=xTest, mean=mu, sd=sigma)
    lines(xTest, pdfX[, i], pch="", lty=2, col="blue", lwd=4)
}
lines(xTest, rowSums(pdfX), pch="", lty=1, lwd=4)
#dev.off()
```

The problem is that we do not know *a priori* how many clusters our data contains. 
Psorakis et al. developed a rigourous approach to automatically estimate this, however it
is beyond the scope of this note. Here, instead we rely on a simple cluster validity
metric, the BIC (Bayesian Information Criterion), and choose $K$ to be the "knee" point of
the scree plot (recall that the ``true" number of clusters is inherently ambigouos). 

```{r, warning=FALSE, message=FALSE, cache=TRUE, fig.width=6, fig.height=6, fig.align='center'}
par(mfrow=c(1, 1))
iDay <- 2
startSec <- (iDay-1)*24*60*60 # 1 day x 24 hrs x 60 mins x 60 secs
stopSec <- (iDay)*24*60*60
thisData <- data[data$relativeTime >= startSec & data$relativeTime < stopSec, ]
fit <- Mclust(data=thisData$relativeTime, G=2:200, modelNames="V")
bic <- as.numeric(fit$BIC)
#pdf("BIC.pdf")
plot(2:200, bic, type="p", pch=19, xlab="Number of clusters", 
     ylab="Bayesian Information Criterion (BIC)",
     cex.lab=1.3, cex.axis=1.3, cex.main=1.3, cex.sub=1.3)
K = 115 # chosen number of clusters
abline(v=K, col="red", lty=2, lwd=4)
#dev.off()
fit <- Mclust(data=thisData$relativeTime, G=K, modelNames="V")
```

Now that we have a fitted GMM we can generate the `responsibilityMatrix`
(observation-to-cluster matrix); a $Z \times K$
matrix where $Z$ is the total number of observations and $K$ is the number of gathering 
events (clusters). If observation $z$ is part of cluster $k$ then 
`responsibilityMatrix[z, k] = 1` otherwise is zero.
         
```{r, warning=FALSE, message=FALSE, cache=TRUE}
get_responsibility_matrix <- function(fit) 
{
        # Initialise variables
        NObs <- length(fit$classification) # total no. of observations
        responsibilityMatrix = matrix(data=0, nrow=NObs, ncol=fit$G)
        # Fill responsibilityMatrix with either 0 or 1
        for (iRow in seq(NObs)) 
        {
                responsibilityMatrix[iRow, fit$classification[iRow]] <- 1
        }
    return(responsibilityMatrix)
}

responsibilityMatrix <- get_responsibility_matrix(fit)
```

## 2) Convert responsibility matrix to bird-to-cluster matrix

Multiple observations $z$ correspond to the same bird. The next step is to collapse
the responsibility matrix $Z \times K$ to a bird-to-cluster matrix `birdMatrix`;a $N \times K$, where $N$ is
the number of *unique* `birdID` by summing the occurences of the same bird across the 
same gathering event.

```{r, warning=FALSE, message=FALSE, cache=TRUE}
responsibility_matrix_to_bird_matrix <- function(responsibilityMatrix, birdID)
{
    # Initialise variables
    NBirds <- length(levels(birdID)) # no. of unique birds
    K <- dim(responsibilityMatrix)[2] # no. of gathering events
    birdMatrix <- matrix(data=0, nrow=NBirds, ncol=K)
    uniqueBirds <- levels(birdID)
    rownames(birdMatrix) <- uniqueBirds
    # Loop through every unique bird
    for (iBird in seq(NBirds)) 
    {
        # Extract responsibility matrix for this birdID
        thisBird <- responsibilityMatrix[birdID==uniqueBirds[iBird], ]
        if (class(thisBird)=="numeric") # apply() fails if iBird only has one row
        {
            birdMatrix[iBird, ] <- thisBird
        } else
        {
            birdMatrix[iBird, ] <- apply(thisBird, 2, sum)  
        }
    }
    return(birdMatrix)
}

birdMatrix <- responsibility_matrix_to_bird_matrix(responsibilityMatrix, thisData$birdID)
```

## 3) Convert bird-to-cluster matrix to adjacency matrix

Last step is to convert the bird-to-cluster matrix $N \times K$ to the `adjacencyMatrix`
$N \times N$. `adjacencyMatrix[i, j]` is defined as the co-occurence of birds $i$ and $j$,
that is, the number of times they were recorded in the same feeding event.

```{r, warning=FALSE, message=FALSE, cache=TRUE}
bird_matrix_to_adjacency_matrix <- function(birdMatrix)
{
    # Initialise variables
    NBirds <- dim(birdMatrix)[1]
    adjacencyMatrix <- matrix(data=0, nrow=NBirds, ncol=NBirds)
    rownames(adjacencyMatrix) <- rownames(birdMatrix)
    colnames(adjacencyMatrix) <- rownames(birdMatrix)
    for (iBird1 in seq(NBirds))
    {
        for (iBird2 in seq(NBirds))
        {
            if (iBird1 == iBird2)
            {
                # If it's the same bird then no link
                adjacencyMatrix[iBird1, iBird2] <- 0
            } else
            {
                # Count the number of co-occurences for the same feeding event
                thisPair <- birdMatrix[c(iBird1, iBird2), ]
                adjacencyMatrix[iBird1, iBird2] <- sum(apply(thisPair, 2, min))
                adjacencyMatrix[iBird2, iBird1] <- adjacencyMatrix[iBird1, iBird2] 
            }
        }
    }
    return(adjacencyMatrix)
}

adjacencyMatrix <- bird_matrix_to_adjacency_matrix(birdMatrix)
```

## 4) Display network

The identified adjacency matrix may contain spurious connections, because two birds 
may have been at the feeder at the same time by coincidence rather than because they 
are socially affiliated (especially during peak feeding events). Psorakis et al.
derived a rigorous statistical test to define whether a connection is spurious or not, 
however it is beyond the scope of this note. Instead we use a simple cut-off and remove
connections which are low compared to the rest.

```{r, warning=FALSE, message=FALSE, cache=TRUE, fig.width=8, fig.height=8, fig.align='center'}
# Retrieve connection weights from the adjacency matrix
N <- dim(adjacencyMatrix)[1]
linkWeight <- matrix(data=adjacencyMatrix, ncol=1, nrow=N*N) #
linkWeight <- linkWeight[linkWeight!=0] # remove weights which are already zero

# Plot histogram of weights and find the mode
hist(linkWeight, col="grey", border="white", breaks=100, freq=F, 
     xlab="Adjacency matrix weight", ylab="Frequency", main="")
pdfWeights <- density(linkWeight) # fit probability density function (pdf)
lines(pdfWeights) # plot fitted pdf
modeWeight <- pdfWeights$x[which.max(pdfWeights$y)] # find the mode
abline(v=modeWeight, col="red", lty=2)

# Set any connection less than the mode to zero and plot network
myAdjacencyMatrix <- adjacencyMatrix
myAdjacencyMatrix[myAdjacencyMatrix <= modeWeight] <- 0
thisNet = network(myAdjacencyMatrix, directed=FALSE, matrix.type="adjacency")
plot(thisNet, displaylabels=TRUE, label.cex=0.5, displayisolates=F, edge.lwd=myAdjacencyMatrix/10)
```

# Overall social network

Let us now repeat the social network identification workflow for all days in our dataset
and then combine all the adjacency matrices together.

```{r, warning=FALSE, message=FALSE, cache=TRUE, fig.width=8, fig.height=8, fig.align='center'}
NDays <- ceiling(max(data$relativeTime)/60/60/24) # total no. of days in our dataset
NBirds <- length(levels(data$birdID)) # no. of unique birds
adjacencyMatrix <- array(data=0, dim=c(NBirds, NBirds, NDays)) # an adjacency matrix for every day
# Loop through all days
for (iDay in seq(NDays))
{
    startSec <- (iDay-1)*24*60*60 
    stopSec <- (iDay)*24*60*60
    thisData <- data[data$relativeTime >= startSec & data$relativeTime < stopSec, ]
    if (dim(thisData)[1] > 10) # don't try to cluster if only a handful of times are available 
    {
        fit <- Mclust(data=thisData$relativeTime, G=seq(from=2, to=200, by=2), modelNames="V")
        responsibilityMatrix <- get_responsibility_matrix(fit)
        birdMatrix <- responsibility_matrix_to_bird_matrix(responsibilityMatrix, thisData$birdID)
        adjacencyMatrix[, , iDay] <- bird_matrix_to_adjacency_matrix(birdMatrix)   
    }
}

# Combine adjacency matrix from every day
overallAdjacencyMatrix <- apply(adjacencyMatrix, c(1, 2), sum)
N <- dim(overallAdjacencyMatrix)[1]
linkWeight <- matrix(data=overallAdjacencyMatrix, ncol=1, nrow=N*N) #
linkWeight <- linkWeight[linkWeight!=0] # remove weights which are already zero

# Plot histogram of weights and find the mode
hist(linkWeight, col="grey", border="white", breaks=100, freq=F, 
     xlab="Adjacency matrix weight", ylab="Frequency", main="")
pdfWeights <- density(linkWeight) # fit probability density function (pdf)
lines(pdfWeights) # plot fitted pdf
modeWeight <- pdfWeights$x[which.max(pdfWeights$y)] # find the mode
abline(v=modeWeight, col="red", lty=2)
```

```{r, warning=FALSE, message=FALSE, cache=TRUE, fig.width=11, fig.height=11, fig.align='center'}
# Set any connection less than the mode to zero and plot network
myAdjacencyMatrix <- overallAdjacencyMatrix
myAdjacencyMatrix[myAdjacencyMatrix <= modeWeight] <- 0
thisNet = network(myAdjacencyMatrix, directed=FALSE, matrix.type="adjacency")
plot(thisNet, displaylabels=TRUE, label.cex=0.5, displayisolates=F, edge.lwd=myAdjacencyMatrix/10)
```

For some of these birds we have information about which nest boxes they occupy. We can 
therefore plot the above social network spatially by placing the nodes at the known nest boxes
co-ordinates (note this is a reduced social network as we only have this info for a subset
of all RFID-tagged birds)

```{r, warning=FALSE, message=FALSE, cache=TRUE, fig.width=11, fig.height=11, fig.align='center'}
library(OpenStreetMap)
library(igraph)

#INPUTS
adj_mat<-myAdjacencyMatrix
indivs<-paste0("01", uniqueBirdID) # Append "01" to match IDs in "2015_PEN_box_owners" (it's antennae ID)
dimnames(adj_mat)<-list(indivs,indivs)
box_owners<-read.csv("2015_PEN_box_owners.csv",header=TRUE)
juvs<-read.csv("PEN2015_juvs.csv",header=TRUE)  #JUVENILE LIFE HISTORY INFORMATION
all<-rbind(box_owners,juvs)

#FIND BOX OWNERS AND THEIR OFFSPRING THAT ARE IN NETWORK
find_foc<-which(indivs %in% as.character(all[,"RFID"]) )
foc<-rep(1,length(indivs))
foc[find_foc]<-2
box_ids<-indivs[foc==2]

#CLIP ADJACENCY MATRIX TO REMOVE NON-BOX INDIVIDUALS
clipped_mats<-as.matrix(adj_mat[box_ids,box_ids])
clipped_all<-all[which(all[,"RFID"] %in% box_ids),]
clipped_all<-clipped_all[with(clipped_all,order(-LAT,LON)),]
rerd<-as.numeric(match(clipped_all[,"RFID"],box_ids))
clipped_mats<-clipped_mats[rerd,rerd]

#CREATE FACTORS FOR SETTING GRAPH ATTRIBUTES
sex_temp<-as.character(clipped_all[,"SEX"])
sex_temp[which(is.na(sex_temp))]<-"UNK"
clipped_all[,"SEX"]<-sex_temp
sex_num<-factor(sex_temp,labels=c("1","2","3"))
cols<-c("red","blue","yellow")
age_temp<-rep(1,nrow(clipped_all))
age_temp[which(clipped_all[,"PAIR"]==0)]<-2
shapes<-c("circle","square")

#CREATE IGRAPH OBJECT AND SET VERTEX ATTRIBUTES
adj_mat_2<-graph.adjacency(clipped_mats,mode=c("undirected"),weighted=TRUE,diag=FALSE)
V(adj_mat_2)$color<-cols[sex_num]
V(adj_mat_2)$shape<-shapes[age_temp]

#SET EDGE ATTRIBUTES
E(adj_mat_2)$width<-E(adj_mat_2)$weight/40
box_c<-lapply(split(all,all[,"BOX"]),function(x) as.vector(outer(x[,"RFID"], x[,"RFID"], paste, sep="-")))
box_c<-as.character(unlist(box_c))  #GET ALL POSSIBLE RELATED/PAIRED EDGES
edge_list_2<-apply(get.edgelist(adj_mat_2), 1, paste, collapse="-")
E(adj_mat_2)$color<-ifelse(edge_list_2 %in% box_c,"green","black")

#REMOVE ISOLATES (INDIVIDUALS WITH NO ASSOCIATION)
deg_2<-degree(adj_mat_2,mode="all")
names(deg_2)<-NULL
inds_2<-which(as.numeric(deg_2)==0)
removals<-as.character(V(adj_mat_2)$name[inds_2])
removals<-c(removals,"010C109B7E","010C11BC8D")
adj_mat_2<-delete_vertices(adj_mat_2,removals)
clipped_all<-clipped_all[!clipped_all[,"RFID"] %in% removals,]
coords<-as.matrix(cbind(clipped_all[,c("LAT","LON")],ind=seq(1:nrow(clipped_all))))

#CALCULATE PLOT PARAMETERS
min_window<-0.000075
temp_lat<-as.numeric(c(max(coords[,1]),min(coords[,1])))
temp_lon<-as.numeric(c(min(coords[,2]),max(coords[,2])))
box_size_lat<-abs(diff(temp_lat))*(min_window/abs(diff(temp_lat)))
box_size_lon<-abs(diff(temp_lon))*(min_window/abs(diff(temp_lon)))
lat<-c(temp_lat[1]+box_size_lat,temp_lat[2]-box_size_lat)
lon<-c(temp_lon[1]-box_size_lon,temp_lon[2]+box_size_lon)
vert_size.1<-box_size_lat

#JITTER VERTEX COORDINATES TO PREVENT OVERLAP AND GENERATE GRAPH LAYOUT
jitter<-0.00005         
alt_mat<-matrix(c(0,0,0,jitter,0,(-1*jitter),(-1*jitter),0,jitter,0),ncol=2,byrow=TRUE)
secondary<-matrix(c(jitter,jitter,(-1*jitter),(-1*jitter),(-1*jitter),jitter,jitter,(-1*jitter)),ncol=2,byrow=TRUE)
all_mat<-rbind(secondary,alt_mat)
spl_co<-split(as.data.frame(coords),list(coords[,1],coords[,2]))
spl_co<-spl_co[lapply(spl_co,nrow)>0]
names(spl_co)<-NULL
rect_pos<-lapply(spl_co,function(x) x[1,1:2])
rect_df<-do.call(rbind,rect_pos)
rect_temp<-lapply(spl_co,function(x) x[1,])
coord_alt<-lapply(spl_co,function(x) cbind(as.matrix(x[,1:2])+all_mat[1:nrow(x),],ind=x[,"ind"]))
coord<-do.call(rbind,coord_alt)
coord<-coord[order(coord[,"ind"]),]
row.names(coord)<-NULL
coords<-as.matrix(coord[,c(2,1)])   

#CREATE RECTANGLES FOR PLOT
divergence<-box_size_lat     
rect_1<-as.numeric(rect_df[,2])-divergence
rect_2<-as.numeric(rect_df[,1])-divergence
rect_3<-as.numeric(rect_df[,2])+divergence
rect_4<-as.numeric(rect_df[,1])+divergence
names(rect_1)<-names(rect_2)<-names(rect_3)<-names(rect_4)<-NULL

#SPATIAL PLOT OF NETWORK
#tiff("SpatialNetwork.tiff",width=40,height=40,units="mm",res=1200,pointsize=3)
par(pty="s",usr=c(lon[1],lon[2],lat[2],lat[1]),mar=c(4,4,4,4))
plot(lon[1]:lon[2],lat[2]:lat[1],type="n",xlim=c(lon[1],lon[2]),ylim=c(lat[2],lat[1]),xlab="Longitude",ylab="Latitude")
#plot(pen_proj)
legend("topright",inset=c(0,0),legend=c("Adult Female","Adult Male","Juvenile (Unknown Sex)","Related or Paired","Unrelated","Location of Feeder"),pch=c(16,16,15,NA,NA,18),lty=c(NA,NA,NA,1,1,NA),bg="white",col=c(cols,"green","black","pink"),pt.bg=c(cols,"green","black","pink"),cex=0.75,ncol=1,text.col="black",lwd=0.2)
plot.igraph(adj_mat_2,layout=coords,vertex.label=NA,vertex.size=vert_size.1*50,rescale=FALSE,xlim=c(lon[1],lon[2]),ylim=c(lat[2],lat[1]),add=TRUE,vertex.frame.color=NA)
rect(rect_1,rect_2,rect_3,rect_4,border="green",lwd=0.3)
points(x=-5.1692,y=50.1989,pch=18,col="pink",cex=2) # LOCATION OF FEEDER
#dev.off()
```
